Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Quasiperiodic Variables from TESS

### 2023-08-15 paper/ms.tex
update ms: add binarity section

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.96\textwidth]{f2.pdf}
		\vspace{-0.3cm}
		\caption{
			{\bf Validation plots used to  label CQVs}.  The complete figure
			set, with one image per sector for each of the \nallcands\
      objects in Table~\ref{tab:thetable}
			is available online {\bf For internal collaboration review:
				\url{https://www.dropbox.com/sh/khtwk5a6z0zgrif/AABRG21Ire7VS4BUnaD1hOR8a?dl=0}}.
			Panels are as follows.
			{\it a)}: Phase-folded light curve; gray points are raw 2-minute
			data and black points are binned to 200 points per cycle.
			{\it b)}: Phase-dispersion minimization (PDM) periodogram.
			Dotted lines show up to the 10$^{\rm th}$ harmonic and
			subharmonic.
			{\it c)}: DSS finder chart, with 1- and 2-TESS pixel radius
			circles displayed for scale.
			{\it d)}: Cleaned light curve, binned to 20-minute cadence, in
			Barycentric TESS Julian Date (BTJD).
			{\it e)}: Phase-folded light curve, binned to 100 points per
			cycle.  The gray line denotes the automated spline-fit to the
			wrapped phase-folded light curve, and small gray triangles
			denote automatically identified local minima.
			{\it f)}: Phase-folded light curve at twice the peak period.
			{\it g)}: Phase-folded light curve at half the peak period.
			{\it h)}: Phase-folded time-series within the ``background''
			aperture defined in the SPOC light curves.
			{\it i)}: Phase-folded flux-weighted centroid in the column
			direction.
			{\it j)}: Phase-folded flux-weighted centroid in the row
			direction.
			{\it k)}: Gaia DR2 color--absolute magnitude diagram.     
			The gray background denotes stars within 100\,pc.
			{\it l)}: Information from Gaia DR2, TIC8, and the automated
			dip-counting search pipeline.  ``Neighbors'', abbreviated
			``nbhr'', are listed within apparent distances of 2 TESS pixels
			if $\Delta T$$<$2.5.
			{\it m)}: BANYAN-$\Sigma$ v1.2 association probabilities, calculated
			using positions, proper motions, and the parallax.
		}
		\label{fig:vet}
	\end{center}
\end{figure*}

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.98\textwidth]{f3.pdf}
    \vspace{-0.3cm}
		\caption{
      {\bf CQVs found in the TESS 2-minute data.}
      Phased TESS light curves over one month are shown for \ngoods\
      CQVs in the high quality sample.  Gray are raw 2-minute data;
      black bins to 300 points per cycle.  Each panel is labeled by
      the TIC identifier, the TESS sector number, and the period in
      hours.  Objects are ordered such that sources with the most TESS
      data available are on top (see Section~\ref{sec:catalog}).
		}
		\label{fig:cqvs}
	\end{center}
\end{figure*}

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.95\textwidth]{f8.pdf}
		\vspace{-0.1cm}
		\caption{
      {\bf Properties of CQVs identified by our search}.
      CQVs are mostly pre-main-sequence M dwarfs, younger than
      $\approx$150 Myr, with rotation periods faster than
      $\approx$1\,day.  The \ngoods\ bonafide CQVs in
      Table~\ref{tab:thetable} are the dark blue circles; \nmaybes\
      ambiguous CQV candidates are light blue circles.  Cases with
      elevated Gaia DR2 RUWE values are highlighted.
      The top panels show the \nstarssearched\ target stars with
      120-second cadence TESS data as the shaded gray background;
      darker regions correspond to a larger relative number of
      searched stars.  The lower-left panel compares the
      rotation--color distribution of CQVs against the rotation
      periods of K and M dwarfs in the Pleiades from
      \citet{2016AJ....152..114R}.  The lower-middle panel plots the
      derived corotation radii $R_{\rm cr} = (GM/\Omega^2)^{1/3}$ in
      units of stellar radii against the measured CQV periods, in
      units of hours.  Ages in the final panel are known from cluster
      membership.
		}
		\label{fig:catalogscatter}
	\end{center}
\end{figure*}

@@

Table~\ref{tab:thetable} lists the \nallcands\ objects identified by
our search.  The ``high-quality sample'' includes \ngoods\ of these
objects, which demonstrated what we viewed as unambiguous
characteristics of the CQV phenomenon in at least one TESS sector.
The classification of \nmaybes\ CQV candidates was ambiguous, and the
\ndebunked\ remaining objects were false positives that we discuss below.
The \texttt{quality} column in the table divides the three classes;
additional data from TESS or other instruments could help resolve the
classification of the ambiguous cases.   Of the \ncqvsnodebunked\ CQVs
and candidate CQVs, \nbothdipfourier\ were found using both the
dip-counting and Fourier techniques, \nyesdipnofourier\ were found
using only the dip-counting technique, and \nyesfouriernodip\ were
found using only the Fourier technique.  In the following, we will
restrict our discussion to the high-quality sample, irrespective of
discovery method.

@@

In terms of the light curve shapes, Figure~\ref{fig:cqvs} shows a
broad range of variability, with anywhere from two to eight local
minima per cycle.  Some stars show relatively ordinary modulation
during one portion of the phased light curve, and highly structured
modulation in the remainder of the cycle (e.g.  TIC~206544316,
TIC~224283342, TIC~402980664).  Others show structured modulation over
the entire span of a cycle (e.g. TIC~2234692, TIC~401789285,
TIC~425933644, TIC~142173958).  Others show some mix between these two
modes.

@@

For the \ngoodsfieldbanyan\ stars for which BANYAN\,$\Sigma$ did not
find any association, we were not able to confidently associate either
star with any young groups.  Both do seem to show the CQV signal over
multiple TESS sectors, and both are photometrically elevated relative
to the main sequence.  Both were also noted by
\citet{2021ApJ...917...23K} as being in the ``diffuse'' population of
$<$50\,Myr stars near the Sun.

@@

@@

The main types of binarity of interest in this work were those that
could confuse our understanding of CQVs.  For instance, within the
21$''$ TESS pixels, binary companions can produce multiple photometric
signals and hinder our ability to correctly identify the star hosting
the CQV signal.  Binary companions can also bias photometric magnitude
and color measurements, thereby biasing our stellar parameter
estimates.  To attempt to identify binaries, we considered the
following lines of information.
%
\paragraph{Radial velocity scatter}---We examined diagrams of the Gaia
DR3 ``radial velocity error'' as a function of stellar color for all
\ncqvsnodebunked\ CQVs and candidate CQVs.  Since this quantity
represents the standard deviation of the non-published Gaia RV time
series, outliers can suggest single-lined spectroscopic binarity.
These plots showed two clusters of stars, at $\lesssim$10\,\kms and
20-25\,\kms.  We there adopted a threshold of $20$\,km\,s$^{-1}$
to flag possible single-lined spectroscopic binaries, which selected
\nrvscatter\ stars: TIC~405910546, TIC~224283342, and TIC~280945693.
%
\paragraph{RUWE}---We examined plots of Gaia DR3 renormalized unit
weight error (RUWE) as a function of brightness as color.\footnote{For
an explanation of the renormalized unit weight error (RUWE), see the
GAIA DPAC technical note \url{http://www.rssd.esa.int/doc_fetch.php?
id=3757412}.}  Elevated RUWEs imply elevated noise relative to a
single-source astrometric model.  This can be caused by marginally
resolved point sources skewing the single-transit centroid
measurements,  intrinsic photometric variability, or intrinsic
astrometric motion.  Based on this exercise, we adopted a threshold of
RUWE$_{\rm DR3}$ $>$ 2 to flag sources with excess astrometric noise.
This threshold yielded \ngoodhighruwe/\ngoods\ high-quality CQVs with
a Gaia DR2 RUWE$>$2; \nmaybehighruwe/\nmaybes\ of the ambiguous sample
share this characteristic.
%
\paragraph{Gaia DR3 non-single stars}---Gaia DR3 included a
``non\_single\_star'' column that flagged known or suspected
eclipsing, astrometric, and spectroscopic binaries.  None of the stars
in our CQV sample were identified as possible binaries in this column.
%
\paragraph{Multiple periodic TESS signals}---During our visual
analysis of the TESS light curves and PDM periodograms, we flagged
sources with beating light curves, and with PDM periodograms that
showed multiple periods.  We also attempted to disentangle the two
signals by subtracting the mean CQV signal over each sector, and then
repeating the phase-dispersion minization analysis.  The results of
this effort are summarized in the secondary periods, $P_{\rm sec}$,
listed in Table~\ref{tab:thetable}.  {\bf We found additional periods
in XX of the CQVs, of which YY also had elevated RUWEs}.

%FIXME FIXME FIXME:
% Need to actually incorporate into the table!

We incorporated each of these sources of information into a column in
Table~\ref{tab:thetable} that expresses whether any given source
passed each of the binarity indicators.
We discuss some important--and complicated--aspects of the systems
that seem to be binary in Section~\ref{subsec:discbinary}.

@@

Figure~\ref{fig:catalogscatter} shows derived stellar
properties for our CQV catalog, and compares the CQVs against both the
target star sample (top panels), and against stars in the Pleiades
\citep{2016AJ....152..114R}.  Typical CQV masses span
0.1-0.4\,$M_\odot$, and typical ages span 2-150\,Myr.  This mass
and age range includes both fully convective stars
($M_\star$$\lesssim$0.25\,$M_\odot$), and stars with a combination of
radiative cores and convective envelopes
($M_\star$$\gtrsim$0.25\,$M_\odot$; \citealt{2018A&A...619A.177B}).
We found no obvious morphology differences between the two classes,
which is somewhat surprising given that the star's interior structure may influence
the field topology \citep{2009A&A...496..787R}.  In terms of
their rotation rates relative to the Pleiades, the CQVs are among the
more rapidly rotating half of M dwarfs. 
%The dearth of $T$$>$15.5 CQVs
in our sample, despite our search extending to $T$$=$16, is a
consequence of the 120-second selection function, not detection
sensitivity.

@@

\subsection{Binaries, massive CQVs, and a new class of false positive}
\label{subsec:discbinary}

%FIXME FIXME FIXME
%TODO: update to give some flavor for how many sources show second periods!

The high-RUWE objects in Figure~\ref{fig:catalogscatter} tend to be
among the more massive half of the CQV sample.  This suggests that
some of the ``high-mass CQVs'' may be unresolved blends in which the
lower mass companion produces the CQV signal.

@@

The two most massive CQVs in our sample, nominally in the K dwarf mass
regime, present a relevant case study.  To date, the only stars
reported to show the CQV phenomenon are M dwarfs, with typical stellar
masses $\lesssim$0.3\,$M_\odot$
\citep{2017AJ....153..152S,2022AJ....163..144G}.  TIC~405754448 and
TIC~405910546 appear to have masses of $\approx$0.82\,$M_\odot$ and
$\approx$0.60\,$M_\odot$ respectively.  The next-highest masses in our
sample are $\approx$0.40\,$M_\odot$.

Based on their locations locations in the color--absolute magnitude
diagram and membership in LCC, both of the K dwarfs do indeed appear
to be high mass.  However in detail, both are subject to ambiguities
in interpretation.  The light curve morphology of TIC~405910546 is
unique in the CQV sample, and suggestive of an eclipsing binary.
Independently, TIC~405910546 was one of the \nrvscatter\ CQVs flagged
with a Gaia DR3 radial velocity scatter exceeding 20\,\kms.  Combined,
these factors suggest that TIC~405910546 might be a pre-main-sequence
eclipsing binary; it should be studied further to clarify this
classification.  For TIC~405754448, we believe that this source {\it
is} an unresolved binary, because RUWE$_{\rm DR2}$=4.7, and because
the raw light curves in Sectors 11, 37, and 38 show an additional
$\approx$6.5\,day, $\approx$0.3\% amplitude sinusoidal signal
suggestive of an unresolved photometric companion.  If TIC~405754448
is a K+M binary, then the flux ratio between the primary and secondary
would be expected to be $\approx$10:1.  It would be challenging for
the M dwarf to produce the observed 12.9\,hr signal with such a flux
deficit, but not impossible.  While both of these objects suggest that
the CQV phenomenon may extend up in mass to pre-main-sequence K
dwarfs, more data are needed to fully substantiate this claim.

\subsubsection{Systems near the 3:2 commensurability}

\paragraph{TIC~435903839}
We originally classified TIC~435903839, with RUWE$_{\rm DR2}$=11.6, as
an ``ambiguous'' CQV with 
a 10.82\,hr period, because this period minimized the
dispersion in the phase-folded light curve.  However careful inspection
of the periodogram
reveals that this source is a photometric blend of two ordinary
rotating stars with $P_0$=3.60\,hr, and $P_1$=5.41\,hr.  This is a
novel false positive scenario for CQVs: two rapidly-rotating stars
with near-integer ratios of rotation periods.  The beat between the
two rotation signals produces the apparent CQV signal.  Such false
positives can be excluded through careful accounting of all peaks in a
periodogram.  For instance, TIC~435903839 shows a peak at 16.27\,hr,
which is not an integer multiple of the dispersion-minimizing 10.82\,hr period.
This particular case is an ``impostor'' CQV.

\paragraph{TIC~425937691}
TIC~425937691 is an odd converse case: it shows two seemingly independent
CQV signals on what appears to be the same star.  The two signals have
periods of $\approx$4.82\,hr and $\approx$3.22\,hr, and so also fall near
the 3:2 commensurability.
The former is the larger amplitude signal visible in
Figures~\ref{fig:cqvs} and~\ref{fig:evoln}, corresponding to signal
with peak-to-peak amplitude of $\approx$8\%.  The latter signal is
only visible after subtracting the primary period, and it has a
sinusoidal envelope with a peak-to-peak amplitude of 2.5\%, and with
three sharp dips super-posed over each cycle.  For
TIC~425937691, ${\rm RUWE}_{\rm DR2}=2.9$.

Given the two photometric signals and the elevated RUWE, this source is 
probably an unresolved binary consisting of two CQVs.  Recent work has shown that the orbits of
binaries closer than $\lesssim$700 AU tend to be aligned with their
planetary systems \citep{2022AJ....163..207C}.  If we assume that
observing CQV variability similarly requires near edge-on viewing
geometries, then we might expect a sufficiently close binary with one
CQV to also have another, since the spin axes in sufficiently close
binaries would tend to be aligned.  In this scenario, the two periods
being within $\approx$0.2\% of the 3:2 period commensurability would
simply be a coincidence.

@@

With that said, one might expect a truly quasiperiodic process to be
able to explore all phase angles with equal weight.  LP 12-502, and
perhaps other CQVs, seem to have preferred phases.  For LP 12-502, all
of the dips happen over phases corresponding to only two thirds of the
period (Figure~\ref{fig:lp}).  The remaining third seems to be ``out
of limits'' for any dipping material.  This could be evidence that
some aspect the stellar magnetic field is strongly asymmetric, and can
generate and hold extrinsic material at corotation, but only over two
thirds of the equatorial circle.  Alternatively, the source of the
material (e.g. a planetesimal swarm) might be distributed over an arc
of the same angular extent (240$^\circ$).  We favor the former
explanation, for reasons discussed below.

@@

The key difference between the prominence and dust clump scenarios is
in whether the occulting material of interest is
neutral hydrogen, or dust.  In the phrasing of the ``frozen flux''
condition of ideal rigid field magnetohydrodynamics, the tendency of
both to become trapped at the corotation radius in the equatorial
plane is tied to how of the four relevant forces (gravity, Lorentz,
inertial Coriolis, and inertial centrifugal), the Lorentz and Coriolis
only act perpendicular to field lines, while gravity and the
centrifugal force are in balance at $R_{\rm cr}$
\citep[see][Sec.~2]{2005MNRAS.357..251T}.  The magnetic field strength
is only relevant in this formulation of the system in that we must
have $R_{\rm sonic} < R_{\rm cr} < R_{\rm Alfven}$ in order for closed
loops to exist that can support prominences
\citep{2019MNRAS.482.2853J}.  In detail however, the locations of such
magnetic fixed points depends on the star's magnetic field topology
\citep{2023MNRAS.518.4734S}.

@@

CQVs show broadband flux variations that can be 1-2$\times$ deeper in
the blue than in the red
\citep{2017PASJ...69L...2O,2020AJ....160...86B,2022AJ....163..144G,2023MNRAS.518.2921K}.
For neutral hydrogen to produce this effect in absorption, its opacity
must be larger in the blue than in the red.
\citet{1992oasp.book.....G} suggests that this might be
microphysically possible: while bound-bound absorption provides
opacity only at narrow resonant lines, the hydrogen opacity due to
bound-free absorption is ``jagged'' \citep[see][Figure 8.5 and
Eq.~8.8]{1992oasp.book.....G}, such that at temperatures of
$\approx$3{,}000\,K to $\approx$10{,}000\,K the observed chromatic
transit depths might be reproduced.  While bound-free absorption of
${\rm H}^{-}$ seems like it might be important at such cool temperatures, in
detail this opacity source has the {\it opposite sign} from
what is required to produce deeper dips in the blue than in the red.
Thompson scattering is similarly ruled out as a relevant opacity
source, because it is gray.  The final plausible alternative opacity
source is dust, which has the requisite larger absorption
cross-section in the blue than the red \citep{1989ApJ...345..245C}.

>>>>

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.96\textwidth]{f2.pdf}
		\vspace{-0.3cm}
		\caption{
			{\bf Validation plots used to  label CQVs}.  The complete figure
			set, with one image per sector for each of the \nallcands\
      objects in Table~\ref{tab:thetable}
			is available online {\bf For internal collaboration review:
				\url{https://www.dropbox.com/sh/khtwk5a6z0zgrif/AABRG21Ire7VS4BUnaD1hOR8a?dl=0}}.
			Panels are as follows.
			{\it a)}: Phase-folded light curve; gray points are raw 2-minute
			data and black points are binned to 200 points per cycle.
      The adopted period is given in the lower-right corner.
			{\it b)}: Phase-dispersion minimization (PDM) periodogram.
			Dotted lines show up to the 10$^{\rm th}$ harmonic and
			subharmonic.
			{\it c)}: DSS finder chart, with 1- and 2-TESS pixel radius
			circles displayed for scale.
			{\it d)}: Cleaned light curve, binned to 20-minute cadence, in
			Barycentric TESS Julian Date (BTJD).
			{\it e)}: Phase-folded light curve, binned to 100 points per
			cycle.  The gray line denotes the automated spline-fit to the
			wrapped phase-folded light curve, and small gray triangles
			denote automatically identified local minima.
			{\it f)}: Phase-folded light curve at twice the peak period.
			{\it g)}: Phase-folded light curve at half the peak period.
			{\it h)}: Phase-folded time-series within the ``background''
			aperture defined in the SPOC light curves.
			{\it i)}: Phase-folded flux-weighted centroid in the column
			direction.
			{\it j)}: Phase-folded flux-weighted centroid in the row
			direction.
			{\it k)}: Gaia DR2 color--absolute magnitude diagram.     
			The gray background denotes stars within 100\,pc.
			{\it l)}: Information from Gaia DR2, TIC8, and the automated
			dip-counting search pipeline.  ``Neighbors'', abbreviated
			``nbhr'', are listed within apparent distances of 2 TESS pixels
			if $\Delta T$$<$2.5.
			{\it m)}: BANYAN-$\Sigma$ v1.2 association probabilities, calculated
			using positions, proper motions, and the parallax.
		}
		\label{fig:vet}
	\end{center}
\end{figure*}

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.98\textwidth]{f3.pdf}
    \vspace{-0.3cm}
		\caption{
      {\bf CQVs found in the TESS 2-minute data.}
      Phased TESS light curves over one month are shown for \ngoods\
      CQVs in the high quality sample.  Gray are raw 2-minute data;
      black bins to 300 points per cycle.  Each panel is labeled by
      the TIC identifier, the TESS sector number, and the period in
      hours.  Objects are ordered such that sources with the most TESS
      data available are on top (see Section~\ref{sec:catalog}).
      Sources with large apparent scatter in gray typically show
      secondary periods from unresolved binaries, which are enumerated
      in Table~\ref{tab:thetable}.
		}
		\label{fig:cqvs}
	\end{center}
\end{figure*}

@@

Table~\ref{tab:thetable} lists the \nallcands\ objects identified by
our search.  The ``high-quality sample'' includes \ngoods\ objects,
which demonstrated what we viewed as unambiguous
characteristics of the CQV phenomenon in at least one TESS sector.
The classification of \nmaybes\ CQV candidates was ambiguous, and the
\ndebunked\ remaining objects were false positives that we discuss below.
The \texttt{quality} column in the table divides the three classes;
additional data from TESS or other instruments could help resolve the
classification of the ambiguous cases.   Of the \ncqvsnodebunked\ CQVs
and candidate CQVs, \nbothdipfourier\ were found using both the
dip-counting and Fourier techniques, \nyesdipnofourier\ were found
using only the dip-counting technique, and \nyesfouriernodip\ were
found using only the Fourier technique.  In the following, we will
restrict our discussion to the high-quality sample, irrespective of
discovery method.

@@

In terms of the light curve shapes, Figure~\ref{fig:cqvs} shows a
broad range of variability, with anywhere from two to eight local
minima per cycle.  Some stars show relatively ordinary modulation
during one portion of the phased light curve, and highly structured
modulation in the remainder of the cycle (e.g.  TIC~206544316,
TIC~224283342, TIC~402980664).  Others show structured modulation over
the entire span of a cycle (e.g. TIC~2234692, TIC~425933644, TIC~142173958).  Others show some mix between these two
modes.

@@

For the two stars for which BANYAN\,$\Sigma$ did not
find any association, we were not able to confidently associate either
star with any young groups.  Both do seem to show the CQV signal over
multiple TESS sectors, and both are photometrically elevated relative
to the main sequence.  Both were also noted by
\citet{2021ApJ...917...23K} as being in the ``diffuse'' population of
$<$50\,Myr stars near the Sun.

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.95\textwidth]{f8.pdf}
		\vspace{-0.1cm}
		\caption{
			{\bf Properties of CQVs identified by our search}.
			CQVs are mostly pre-main-sequence M dwarfs, younger than
			$\approx$150 Myr, with rotation periods faster than
			$\approx$1\,day.  The \ngoods\ bonafide CQVs in
			Table~\ref{tab:thetable} are the dark blue circles; \nmaybes\
			ambiguous CQV candidates are light blue circles.  
			Unresolved binaries are flagged either if the Gaia DR3 radial
			velocity scatter exceeded 20\,\kms, or if
			Gaia ${\rm RUWE}_{\rm DR3}$$>$2 and multiple photometric signals were present in the
			TESS light curve.
			The top panels show the \nstarssearched\ target stars with
			120-second cadence TESS data as the shaded gray background;
			darker regions correspond to a larger relative number of
			searched stars.  The lower-left panel compares the
			rotation--color distribution of CQVs against the rotation
			periods of K and M dwarfs in the Pleiades from
			\citet{2016AJ....152..114R}.  The lower-middle panel plots the
			derived corotation radii $R_{\rm cr} = (GM/\Omega^2)^{1/3}$ in
			units of stellar radii against the measured CQV periods, in
			units of hours.  Ages in the final panel are known from cluster
			membership.
		}
		\label{fig:catalogscatter}
	\end{center}
\end{figure*}

@@

The main types of binarity of interest in this work were those that
could confuse our understanding of CQVs.  For instance, within the
21$''$ TESS pixels, binary companions can produce multiple photometric
signals and hinder our ability to correctly identify the star hosting
the CQV signal.  Binary companions can also bias photometric magnitude
and color measurements, which would affect our stellar parameter
estimates.  To attempt to identify binaries, we considered the
following lines of information.

{\it Radial velocity scatter}---We examined diagrams of the Gaia
DR3 ``radial velocity error'' as a function of stellar color for all
\ncqvsnodebunked\ CQVs and candidate CQVs.  Since this quantity
represents the standard deviation of the non-published Gaia RV time
series, outliers can suggest single-lined spectroscopic binarity.
These plots showed two clusters of stars, at $\lesssim$10\,\kms and
20-25\,\kms.  We there adopted a threshold of $20$\,km\,s$^{-1}$
to flag possible single-lined spectroscopic binaries, which selected
\nrvscatterflag\ stars: TIC~405910546, TIC~224283342, and TIC~280945693.

{\it RUWE}---We examined plots of Gaia DR3 RUWE as a function of color.\footnote{For
an explanation of the renormalized unit weight error (RUWE), see the
GAIA DPAC technical note \url{http://www.rssd.esa.int/doc_fetch.php?
id=3757412}.}  Elevated RUWEs imply excess noise relative to a
single-source astrometric model.  This can be caused by marginally
resolved point sources skewing the single-transit centroid
measurements,  intrinsic photometric variability, or intrinsic
astrometric motion.  Based on this exercise, we adopted a threshold of
RUWE$_{\rm DR3}$ $>$ 2 to flag sources with excess astrometric noise.
This threshold was met for \ngoodhighruwe/\ngoods\ high-quality CQVs;
\nmaybehighruwe/\nmaybes\ of the ambiguous sample
had this characteristic.
There is some subjectivity in where to set the threshold, since the RUWE distribution has
an extended tail \citep[e.g.][]{2022MNRAS.513.5270P}.
If we had instead required RUWE$_{\rm DR3}$ $>$ 1.4,
\ngoodweakruwe/\ngoods\ high-quality CQVs and \nmaybeweakruwe/\nmaybes\ of the ambiguous sample
would have been flagged.

{\it Gaia DR3 non-single stars}---Gaia DR3 included a
``non\_single\_star'' column that flagged known or suspected
eclipsing, astrometric, and spectroscopic binaries.  None of the stars
in our CQV sample were identified as possible binaries in this column.

{\it Multiple periodic TESS signals}---During our visual
analysis of the TESS light curves and PDM periodograms, we flagged
sources with beating light curves, and with PDM periodograms that
showed multiple periods.  We also attempted to disentangle the two
signals by subtracting the mean CQV signal over each sector, and then
repeating the phase-dispersion minization analysis.  The results of
this effort are summarized in the secondary periods, $P_{\rm sec}$,
listed in Table~\ref{tab:thetable}.  This process yielded \ngoodmultperiodflag/\ngoods\ high-quality CQVs
with secondary periods; \nmaybemultperiodflag/\nmaybes\ of the ambiguous
sample met the same criterion.
Of the \ngoodhighruwe\ good CQVs with RUWE$_{\rm DR3}$ $>$ 2,
\ngoodruweandmultperiod\ also showed secondary periods in the TESS
light curves.
Considering the weaker threshold of 
RUWE$_{\rm DR3}$ $>$ 1.4,
\ngoodweakruweandmultperiod/\ngoodweakruwe\ such CQVs showed secondary TESS periods.

Table~\ref{tab:thetable} summarizes
each of the above sources of information into a single
bitwise column.
We discuss possible connections between binarity and the CQV phenomenon
in Section~\ref{subsec:discbinary}.

@@

Figure~\ref{fig:catalogscatter} shows derived stellar
properties for our CQV catalog, and compares the CQVs against both the
target star sample (top panels), and against stars in the Pleiades
\citep{2016AJ....152..114R}.  Typical CQV masses span
0.1-0.4\,$M_\odot$, and typical ages span 2-150\,Myr.  This mass
and age range includes both fully convective stars
($M_\star$$\lesssim$0.25\,$M_\odot$), and stars with a combination of
radiative cores and convective envelopes
($M_\star$$\gtrsim$0.25\,$M_\odot$; \citealt{2018A&A...619A.177B}).
We found no obvious light curve morphology differences between the two classes.
%which suggests that the star's interior structure may influence
%the field topology \citep{2009A&A...496..787R}.  
In terms of
their rotation rates relative to the Pleiades, the CQVs are among the
more rapidly rotating half of M dwarfs. 
%The dearth of $T$$>$15.5 CQVs
%in our sample, despite our search extending to $T$$=$16, is a
%consequence of the 120-second selection function, not detection
%sensitivity.

@@

\subsection{CQVs and binarity}
\label{subsec:discbinary}

\subsubsection{Binary statistics}

In Section~\ref{subsec:binarity}, we found that a significant fraction
of the CQVs show indications of unresolved binarity.  Excess noise
above the Gaia single-source astrometric model is common
(\ngoodhighruwe/\ngoods\ high-quality CQVs with RUWE$_{\rm DR3}$$>$2),
as is the presence of multiple periods in the TESS light curves
(\ngoodmultperiodflag/\ngoods).  Elevated astrometric noise is almost
always accompanied by multiple detectable TESS periods
(\ngoodruweandmultperiod/\ngoodhighruwe high-quality CQVs).  The
latter point strongly corroborates the idea that most sources with
RUWE$_{\rm DR3}$$>$2 are intermediate separation binaries with
projected apparent separations below 1$''$, and projected physical
separations $\lesssim$50\,AU.

The multiplicity rate of M dwarfs near the Sun is 26.8$\pm$1.4\%
\citep{2019AJ....157..216W}.  Based on the same study, the peak of the
separation distribution decreases from $\approx$49\,AU for
$0.30$-$0.60$\,$M_\odot$ stars, to $\approx$11\,AU for
$0.15$-$0.30$\,$M_\odot$ M dwarfs.  The multiplicity fraction in our
CQV sample seems either consistent or perhaps marginally higher than
the field fraction.  This could plausibly be understood in a physical
framework in which the presence of intermediate-separation binaries
causes early disk dispersal, freeing the star to contract.  The CQV
phenomenon seems to require rapid rotation; thus if binary systems
tend to produce more rapidly rotating stars, we would expect a sample
of CQVs to have a larger binary fraction than the field.

@@

To date, the only stars reported to show the CQV phenomenon are M
dwarfs, with typical stellar masses $\lesssim$0.3\,$M_\odot$
\citep{2017AJ....153..152S,2022AJ....163..144G}.  However the two most
massive CQVs in our sample, TIC~405754448 and TIC~405910546, appear to
have masses of $\approx$0.82\,$M_\odot$ and $\approx$0.60\,$M_\odot$
respectively.  The next-highest masses in our sample are
$\approx$0.40\,$M_\odot$.

Based on their locations locations in the color--absolute magnitude
diagram and membership in LCC, both of the K dwarfs do indeed appear
to be high mass.  However in detail, both are subject to ambiguities
in interpretation.  The TIC~405910546 light curve has a unique shape,
suggestive of an eclipsing binary.  Independently, TIC~405910546 was
one of only \nrvscatterflag\ CQVs flagged with a Gaia DR3 radial
velocity scatter exceeding 20\,\kms.  Combined, these factors suggest
that TIC~405910546 might be a pre-main-sequence eclipsing binary; it
should be studied further to clarify this classification.  For
TIC~405754448, we believe that the source {\it is} an unresolved
binary, because RUWE$_{\rm DR3}$=6.8, and because the raw light curves
in Sectors 11, 37, and 38 show an additional $\approx$6.5\,day,
$\approx$0.3\% amplitude sinusoidal signal suggestive of an unresolved
photometric companion.  If TIC~405754448 is a K+M binary, then the
flux ratio between the primary and secondary would be expected to be
$\approx$10:1.  It would be challenging for the M dwarf to produce the
observed 12.9\,hr signal with such a flux deficit, but not impossible.
While both of these objects suggest that the CQV phenomenon may extend
up in mass to pre-main-sequence K dwarfs, more data are needed to
fully substantiate this claim.

\subsubsection{An astrophysical CQV false positive: TIC~435903839}

We originally classified TIC~435903839, with RUWE$_{\rm DR3}$=17.7, as
an ``ambiguous'' CQV with a 10.8\,hr period, because this period
minimized the dispersion in the phase-folded light curve.  More careful
inspection however showed that this source is an impostor:
this source is a
photometric blend of two ordinary rotating stars with $P_0$=3.60\,hr,
and $P_1$=5.41\,hr, with a beat period $(P_0^{-1} - P_1^{-1})^{-1}$ of
10.8\,hr.  This is a novel false positive scenario for CQVs:
two rapidly-rotating stars with near-integer ratios of rotation
periods.  The beat between the two rotation signals produces the
apparent CQV signal.  Such false positives can be excluded through
careful accounting of all peaks in a periodogram.  For instance,
TIC~435903839 shows a peak at 16.27\,hr, which is not an integer
multiple of the dispersion-minimizing 10.82\,hr period.

\subsubsection{Multiple CQVs in the same system: TIC~425937691 and TIC~142173958}

TIC~142173958 and TIC~425937691 both show evidence for two separate
CQV signals in their TESS light curves.  For TIC~142173958, the
signals are at 11.76\,hr and 12.84\,hr.  For TIC~425937691, they are
at $\approx$4.82\,hr and $\approx$3.22\,hr, near the 3:2
commensurability.  Given that both sources have two photometric
signals and elevated RUWEs, they are probably unresolved binaries
consisting of two independent CQVs.  Recent work has shown that the
orbits of binaries closer than $\lesssim$700 AU tend to be aligned
with their planetary systems \citep[e.g.][]{2022AJ....163..207C}.  If we
assume that observing CQV variability similarly requires near edge-on
viewing geometries, then we might expect a sufficiently close binary
with one CQV to also have another, since the spin axes in sufficiently
close binaries would tend to be aligned.  In this scenario, the two
periods of TIC~425937691 being within $\lesssim$1\% of the 3:2 period
commensurability would simply be a coincidence.

@@

With that said, one might expect a truly quasiperiodic process to be
able to explore all phase angles with equal weight.  LP 12-502, and
perhaps other CQVs, seem to have preferred phases.  For LP 12-502, all
of the dips happen over phases corresponding to only two thirds of the
period (Figure~\ref{fig:lp}).  The remaining third seems to be ``out
of limits'' for any dipping material.  This could be evidence that
the stellar magnetic field is strongly asymmetric, such that it can
hold extrinsic material at corotation, but only over two
thirds of the equatorial circle.  Alternatively, the source of the
material (e.g. a planetesimal swarm) might be distributed over an arc
of the same angular extent (240$^\circ$).  We favor the former
explanation, for reasons discussed below.

@@

The key difference between the prominence and dust clump scenarios is
in whether the occulting material of interest is
neutral hydrogen, or dust.  In the phrasing of the ``frozen flux''
condition of ideal rigid field magnetohydrodynamics, the tendency of
both to become trapped at the corotation radius in the equatorial
plane is tied to how of the four relevant forces (gravity, Lorentz,
inertial Coriolis, and inertial centrifugal), the Lorentz and Coriolis
only act perpendicular to field lines, while gravity and the
centrifugal force are in balance at $R_{\rm cr}$
\citep[see][Sec.~2]{2005MNRAS.357..251T}.  The magnetic field strength
is only relevant in this formulation of the system in that we must
have $ R_{\rm cr} < R_{\rm Alfven}$ in order for closed
loops to exist that can support prominences
\citep[e.g.][]{1985Ap&SS.116..285N,2019MNRAS.482.2853J}.  In detail however, the locations of such
magnetic fixed points depends on the star's magnetic field topology.

@@

CQVs show broadband flux variations that can be 1-2$\times$ deeper in
the blue than in the red
\citep{2017PASJ...69L...2O,2020AJ....160...86B,2022AJ....163..144G,2023MNRAS.518.2921K}.
For neutral hydrogen to produce this effect in absorption, its opacity
must be larger in the blue than in the red.
\citet{1992oasp.book.....G} suggests that this might be
microphysically possible: while bound-bound absorption provides
opacity only at narrow resonant lines, the hydrogen opacity due to
bound-free absorption is ``jagged'' \citep[see][Figure 8.5 and
Eq.~8.8]{1992oasp.book.....G}, such that at temperatures of
$\approx$3{,}000\,K to $\approx$10{,}000\,K the observed chromaticities
might be reproduced.  While bound-free absorption of
${\rm H}^{-}$ seems like it should be important at such cool temperatures, in
detail this opacity source has the {\it opposite sign} from
what is required to produce deeper dips in the blue than in the red.
Thompson scattering is similarly ruled out, because it is gray.
The final plausible alternative opacity
source is dust, which has the requisite larger absorption
cross-section in the blue than the red \citep{1989ApJ...345..245C}.
